Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-10 vesicle_code/docs/permeableVes/main.tex
yny

The governing equations are non-dimensionalized by introducing a length
scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
tension scale $Q = k_b/R_0^2 = 10^{-7}$N/m, and the permeability scale
$W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
variable in vesicle suspensions is the reduced area $\alpha = 4\pi A/L^2
\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
length is conserved by the local inextensibility condition, but the area
is not because of semipermeability. Therefore, the reduced area is
dynamic.

@@

\section*{Vesicle Tensions}
\begin{figure*}[htp]
  \centering
  \ifTikz
    \input{figures/relaxationTensions.tikz}
  \else
    \includegraphics{figures/relaxationTensions.pdf}
  \fi
  \caption{\label{fig:relaxationTensions} Tension of images in
  relaxation.}
\end{figure*}

>>>>

%The governing equations are non-dimensionalized by introducing a length
%scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
%$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
%the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
%R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
%tension scale $Q = k_b/R_0^2 = 10^{-7}$N/m, and the permeability scale
%$W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
%variable in vesicle suspensions is the reduced area $\alpha = 4\pi A/L^2
%\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
%length is conserved by the local inextensibility condition, but the area
%is not because of semipermeability. Therefore, the reduced area is
%dynamic.

The governing equations are non-dimensionalized by using a 
characteristic length scale $R_0 = 10^{-6}$m, a bending stiffness of
$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms. We scale time by $\tau\equiv\mu R_0^3/k_b = 0.5s$, 
the velocity by $R_0/\tau = 2\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$Pa, 
tension by $k_b/R_0^2 = 10^{-7}$N/m, and the permeability by $R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. 
Under this nondimensionalization, a two-dimensional semipermeable vesicle in a viscous fluid is characterized by 
(a) its reduced area $\alpha = 4\pi A/L^2
\in (0,1]$, where $L$ is the vesicle length and $A$ is its area, and 
(b) its permeability $\beta = k_w/W$.
In two dimensions, the membrane length is conserved by the local inextensibility condition, 
but the enclosed area is not because of semipermeability. Therefore, the reduced area is
dynamic.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Vesicle Tensions}
\begin{figure*}[htp]
  \centering
  \ifTikz
    \input{figures/relaxationTensions.tikz}
  \else
    \includegraphics{figures/relaxationTensions.pdf}
  \fi
  \caption{\label{fig:relaxationTensions} Tension of vesicles in
  relaxation.}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \ifTikz
    \input{figures/stenosisTensions.tikz}
  \else
    \includegraphics{figures/stenosisTensions.pdf}
  \fi
  \caption{\label{fig:stenosisTensions} Tension of vesicles in
  stenosis.}
\end{figure*}
